MSHS COVID-19 Vaccinations

### 2022-01-10 Combined Dashboard Arrived and Sched Appts.Rmd
Update analysis reference file to include school based practices and update logic for adult vs peds based on the vaccines these pods administer.

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-12-10.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-12-10.xlsx"),
                           sheet = "Pod Mappings Simple")

>>>>

# Import reference data for site and pod mappings
site_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                   "Automation Ref 2021-12-20.xlsx"),
                            sheet = "Site Mappings")
pod_mappings <- read_excel(paste0(user_directory, "/ScheduleData/",
                                  "Automation Ref 2021-12-20.xlsx"),
                           sheet = "Pod Mappings Simple")
